Treatment Outcome Visualization

### 2023-09-16 Paper_stuff.Rmd
Trying to figure out treatment responders

                                      "1"="Inpatient",
                                      "2"="PHP",
                                      "3"="APS",
                                      "4"="Psychatrist",
                                      "5"="PCP",
                                      "6"="Another Physican",
                                      "7"="Therapist",
                                      "17"="Other"

@@

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                       ifelse(is.na(Days_complete_1), NA, "4"
                              ))))),
                    Duration = as.factor(recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      )))

@@

@@

@@

# df without NAs in date and disorder type
Mothership_Diag <- Mothership %>%
  filter(!is.na(Disorder_Type))%>%
  filter(!is.na(TxYear))

Mothership_Diag_treat <- Mothership %>%
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

@@

@@

Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Variable","Total Sample")
Demo_tab

#Disorder Table
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab
```
### Visualization – most common diagnoses.
```{r}
#frequency

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()

# ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
#   geom_bar()+
#   ggtitle("Frequency of Psychiatric Disorder Subtypes") +
#   theme(axis.text.x = element_text(angle = 45,hjust = 1),
#         legend.position = "none")+
#   xlab("Psychiatric Disorder Subtype")+
#   theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   scale_y_continuous(name = "Frequency",limits=c(0,2000))+
#   coord_flip()+
#   facet_wrap(~Duration)
```

```{r}
# Visualization of percent

@@

•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.

@@

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))
```

### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

@@

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
  coord_flip()
```

@@

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

@@

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

>>>>

                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "17"="Other",
                                      "11"="Other",
                                      "0" ="Other"

@@

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                       ifelse(is.na(Days_complete_1), NA, "4"
                              ))))),
                    Duration_lab = as.factor(recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      )),
                    Duration_10 = as.factor(
                      ifelse(Duration == 1 | Duration == 2, "1",
                      ifelse(Duration == 3 | Duration == 4, "2", NA)
                      )))

@@

Disorder_varaibles

@@

# df without NAs in date and disorder type
Mothership_Diag <- Mothership |>
  filter(!is.na(Disorder_Type)) |>
  filter(!is.na(TxYear))

Mothership_Diag_treat <- Mothership |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

Main_Treat <- Mothership |>

@@

@@

Pre_Post
```{r}
Mothership_post <- Mothership |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40,
         !Days_complete_1 == 0,
         !is.na(BL_CUXOS),
         !is.na(SUManx_DC),
         BL_CUXOS > 1,
         SUManx_DC > 0,
         !is.na(BL_CUDOS),
         !is.na(SUMdep_DC),
         BL_CUDOS > 1,
         SUMdep_DC > 0
         ) |>
  mutate(
    Delta_Anx_DC = BL_CUXOS - SUManx_DC,
    Delta_Dep_DC = BL_CUDOS - SUMdep_DC,
    Percent_anx_change = SUManx_DC - BL_CUXOS/BL_CUXOS,
    Percent_Dep_Dchange = SUMdep_DC - BL_CUDOS/BL_CUDOS,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(BL_CUXOS > 10 &(Delta_Anx_DC/BL_CUXOS) <= .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(BL_CUDOS > 10 & (Delta_Dep_DC/BL_CUDOS) <= .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse", 
      ifelse(BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS <= 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & (Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
      ifelse((Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 &(Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0 & (Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Both_Responder", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Both Unresponder",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Dep Unresponders", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5, "Anx Unresponders", "Low Baseline"
      ))))))))))

summary(Mothership_post$Treatment_Responder)
summary(Mothership_post$Anx_Responder)
summary(Mothership_post$Dep_Responder)

ggplot(Mothership_post, aes(x = Treatment_Responder)) +
  geom_bar() +
  coord_flip() +
  labs(
    title = "Treatment response of Anxiety and Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Anx_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Anxiety",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Dep_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

mean(Mothership_post$Percent_anx_change)
ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_anx_change)) +
         geom_boxplot()
#2. Create pre_scores
      # CUXOS_pre = Day1_CUXOS,
      # CUDOS_pre = Day1_CUDOS
      # )

sum(Mothership_post$SUManx_DC < 0)

@@

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Variable","Total Sample")
Demo_tab

#Disorder Table - duratin
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab

#Disorder Tab by 10 days
Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_Diag_treat))
colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
Dis_tab_10

```
### Visualization – most common diagnoses.
```{r}
#frequency

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type))))+
  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
                               ))+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  #scale_fill_manual(values = c("#003f5c","#2f4b7c","#665191", "#a05195", "#d45087", "#f95d6a", "#ff7c43", "#ffa600", "#EBC500")) +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type)),fill= Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1750))+
  scale_fill_manual(values = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
                               )) +
  coord_flip()+
  facet_wrap(~Duration,labeller = labeller(Duration =
      c("1" = "1-5 Days", 
        "2" = "6-10 Days", 
        "3" = "11-15 Days",
        "4" = "16+ Days")
      ))
```

# Most co-ocurring diagnoses
```{r}
# Visualization of percent

@@

•	Visualization – RDQ pre and post change.

```{r}
#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

#Make This Data Set Long Data
library(tidyr)
Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

#Create a Time Variable
Mothership_Long_RDQ$PrePost <- NA
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"

#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
  group_by(rm,PrePost) %>%
  summarise(RDQ=mean(RDQ,na.rm=TRUE))

#Add a Paired Variable to the New Data Set
Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
                            paired=case_when(rm=="rdqPRE_coping"~"1",
                                             rm=="rdqPOST_coping"~"1",
                                             rm=="rdqPRE_pmh"~"2",
                                             rm=="rdqPOST_pmh"~"2",
                                             rm=="rdqPRE_func"~"3",
                                             rm=="rdqPOST_func"~"3",
                                             rm=="rdqPRE_wbs"~"4",
                                             rm=="rdqPOST_wbs"~"4",
                                             rm=="rdqPRE_sym"~"5",
                                             rm=="rdqPOST_sym"~"5"))

#Pre Post RDQ Plot - combined 
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
  #                              "4"="#00BCA3","5"="#008570"),
  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms"))

# pre post RDQ Plot - facet wrap
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost))) +
  geom_point(size=2.5) +
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
  scale_x_discrete(name="Time Point") +
  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
  theme(panel.background=NULL) +
  theme(legend.position="none") +
  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
  #                              "4"="#00BCA3","5"="#008570")) +
  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
  facet_wrap(~paired, labeller = labeller(paired =
    c("1" = "Coping Skills",
      "2"="Positive Mental Health",
      "3"="Functioning",
      "4"="Well-Being",
      "5"="Symptoms")))

•	Table or Visualization – Reasons for discharge results.

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
                               ))+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
  coord_flip()

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
  geom_bar()+ #fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"))+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,2100)) +
  #scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  coord_flip() +
  facet_wrap(~Duration,labeller = labeller(Duration =
      c("1" = "1-5 Days", 
        "2" = "6-10 Days", 
        "3" = "11-15 Days",
        "4" = "16+ Days")
      ))

@@

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()
```

### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
  coord_flip()
```

@@

@@

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
  coord_flip()
```

@@

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
  coord_flip()
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()

### 2023-09-16 Treatment_Outcomes.Rmd
Trying to figure out treatment responders

#Pre Post RDQ Plot
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                              "4"="#00BCA3","5"="#008570"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms"))

>>>>

str(Mothership_Mean_RDQ$rm)

#Pre Post RDQ Plot - combined 
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                               "4"="#00BCA3","5"="#008570"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms"))

# pre post RDQ Plot - facet wrap
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost))) +
  geom_point(size=2.5) +
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
  scale_x_discrete(name="Time Point") +
  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
  theme(panel.background=NULL) +
  theme(legend.position="none") +
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                               "4"="#00BCA3","5"="#008570")) +
  facet_wrap(~paired, labeller = labeller(paired =
    c("1" = "Coping Skills",
      "2"="Positive Mental Health",
      "3"="Functioning",
      "4"="Well-Being",
      "5"="Symptoms")))
```
